How to Avoid OOTA Without Really Trying

### 2024-10-09 paper/ootavacuous.tex
ootavacuous: Add atomic-optimization caution to summary
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\section{Summary and Conclusion}
\label{sec:Summary and Conclusion}

@@

The conclusion to be drawn from this work is that in this context,
avoiding OOTA cycles requires no changes to the standard,
to current implementions, or to user practices for portable code.

>>>>

\section{Summary and Conclusions}
\label{sec:Summary and Conclusions}

@@

One conclusion to be drawn from this work is that in this context,
avoiding OOTA cycles requires no changes to the standard,
to current implementions, or to user practices for portable code.
This work also demonstrates the need for caution when optimizing
atomic operations.
